Full title of the paper (Capitalized)

### 2022-03-07 Paper_Draft1/Draft1.Rmd
adding text and figures to draft

---
title: Full title of the paper (Capitalized)
author:
  - name: Amrita Acharya
    affil: 1,2,\ddagger,*
  - name: Dianne Caravela
    affil: 2, \dagger, \ddagger
  - name: Eunice Kim
    affil: 3
  - name: Emma Kornberg
    affil: 4
  - name: Elisabeth Nesmith
    affil: 5
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
    email: aacharya@smith.edu
  - num: 2
    address: |
      Smith College
    email: dcaravela@smith.edu
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
csl: ../resources/chicago-author-date.csl
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

@@

A recidivist is a term to describe criminals who re-offend.

@@

The data we are using for this project is the Correctional Offender Management Profiling for Alternative Sanctions (COMPAS) Recidivism Risk Scores dataset from AIF360. Northpointe created COMPAS as a commercial risk assessment tool to score defendants on their potential recidivism and violent recidivism risk. The COMPAS dataset we are using has 6,167 rows and each row represents an arrest charge for a defendant. We also have data on the defendant's age, race, sex, what they were charged with, and whether or not the defendant ultimately recidivated.

>>>>

---
title: Full title of the paper (Capitalized)
author:
  -author:
  - name: Amrita Acharya
    affil: 1, 2
  - name: Dianne Caravela
    affil: 1, 3
  - name: Eunice Kim
    affil: 1, 4
  - name: Emma Kornberg
    affil: 1, 5
  - name: Elisabeth Nesmith
    affil: 1, 6
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
  - num: 2
    email: aacharya@smith.edu
  - num: 3
    email: dcaravela@smith.edu
  - num: 4
    email: ekim89@smith.edu
  - num: 5
    email: ekornberg@smith.edu
  - num: 6
    email: enesmith@smith.edu
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
csl: ../resources/chicago-author-date.csl
appendix: appendix.tex

abstract: |
  A variety of disciplines use risk assessment instruments to help humans make data-driven decisions. Northpointe, a software company, created a risk assessment instrument known as the Correctional Offender Management Profiling for Alternative Sanctions (COMPAS). COMPAS uses various behavioral and psychological metrics related to recidivism to assist justice systems in assessing a defendant’s potential recidivism risk. ProPublica published an article which concludes that the biases in the criminal justice system are reflected in the COMPAS software. Using a human rights framework adopted from the organization Women at the Table, we use various debiasing algorithms to analyze both sides of the argument between Northpointe and ProPublica and determine the level and extent of racial bias in the COMPAS algorithm. 
output: rticles::mdpi_article
---

@@

Women @ the Table, the sponsor organization for this project, is “a growing, global gender equality & democracy CSO based in Geneva, Switzerland focused on advancing feminist systems change by using the prism of technology, innovation & AI exercising leverage points in technology, the economy, sustainability & democratic governance” [@noauthor_womenthetable_nodate]. We have been asked to collaborate on their AI & Equality [@noauthor_ai_nodate] initiative, tasked with debiasing the COMPAS algorithm [@noauthor_aif360datasetscompasdataset_2018] and producing a corresponding data story that will be added to their library.

The Correctional Offender Management Profiling for Alternative Sanctions (COMPAS) algorithm was created by the private for-profit company Northpointe, also known by its parent company Equivant [@equivant_faq_nodate], to predict defendants’ risk of recidivism. It generates a score that classifies defendants’ risk of recidivism as either low, medium, or high [@angwin2016machine]. Jurisdictions across the United States use the COMPAS risk assessment instrument. In 2016, ProPublica published a piece that analyzed the methods and algorithms used by Northpointe to uncover racial biases in defendants’ scores [@angwin2016machine]. Their analysis looks at the distribution of decile COMPAS scores among Black and white defendants. ProPublica concludes, after using a statistical parity metric on false positives or false negatives, that the algorithm is racially biased [@larson2016we]. Northpointe denies the allegations of racial bias, conducting their own analyses based on different statistical parity metrics [@equivant_response_2018]. Since then, the two parties have had several exchanges, maintaining their original arguments. Currently, the two parties’ disagreement focuses on pretrial Risk Assessment Instruments (RAIs). ProPublica maintains that there are biases in the outcome values, protected attributes, and covariates during Northpointe’s data processing phase. ProPublica accounts for these biases in their analyses, and Northepointe’s response, highlights how ProPublica did not account for base rates of recidivism in their analysis, which are important to understand initial percentages without the presence of other information.

Our project builds on Women at the Table’s various debiasing algorithms to conduct our own analyses on the COMPAS dataset. Based on this analysis, we employ a human rights framework to contribute to the ongoing ProPublica and Northpointe debate and investigate whether or to what extent there is racial bias in the COMPAS algorithm. With a solid understanding of the two sides, we aim to pinpoint the shortcomings of both arguments and correct them in our analyses. We will use various machine learning algorithms including logistic regression, cross validation, and lasso and ridge techniques to choose models. We will summarize our results using the JupyterNotebook framework from Women at the Table, to be used by members of the organization to teach in a workshop setting. We hope that our findings will highlight the importance of checking statistical analyses using varied methods and contribute to the ongoing discussion of the effects of machine biases in the justice system.

@@

The data we are using for this project is the COMPAS General Recidivism Risk Scores dataset from ProPublica used in their original analysis [@larson_propublicacompas-analysiscompas-scores-two-yearscsv_2022]. The COMPAS dataset we are using is from AI Fairness 360 (AIF360) toolkit [@noauthor_trusted-ai_360] which does the same initial preprocessing as ProPublica. The raw data has 6,167 rows and each row represents an arrest charge for a defendant. ProPublica’s COMPAS data includes the defendant's age, race, sex, what they were charged with, and whether or not the defendant ultimately recidivated within a two-year period after their arrest. For the purposes of our project, which endeavors to evaluate the differing effects of the COMPAS algorithm on white defendants and Black defendants, we have filtered the data to only include individuals whose race is listed as Caucasian or African-American. Our data therefore has 5,723 rows (Figure \ref{fig:table snip}), with the below distributions of race (Figure \ref{fig:race plot}), age (Figure \ref{fig:age plot}), and two year recidivism rate (Figures \ref{fig:recid plot} & \ref{fig:recid race plot}).

```{r table snip, fig.align='center', fig.cap= 'This table is a snippet the data set we will be using.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/table_snippet.png")
```

```{r race plot, fig.align='center', fig.cap= 'This plot shows the distribution of defendant races.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/race_bar_plot.png")
```

```{r age plot, fig.align='center', fig.cap= 'This plot shows the distribution of defendant ages by race.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/race_age_plot.png")
```

```{r recid plot, fig.align='center', fig.cap= 'This plot shows the distribution of two year recidivism outcomes.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/recid_bar_plot.png")
```

```{r recid race plot, fig.align='center', fig.cap= 'This plot shows the distribution of two year recidivism outcomes by race.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/race_recid_plot.png")
```

### 2022-03-07 Paper_Draft1/Draft1.tex
adding text and figures to draft

% Authors, for the paper (add full first names)
\Author{Amrita Acharya$^{1,2,\ddagger,*}$, Dianne Caravela$^{2, \dagger,
\ddagger}$, Eunice Kim$^{3}$, Emma Kornberg$^{4}$, Elisabeth
Nesmith$^{5}$}

% Authors, for metadata in PDF
\AuthorNames{Amrita Acharya, Dianne Caravela, Eunice Kim, Emma
Kornberg, Elisabeth Nesmith}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Statistical and Data Sciences Smith College Northampton, MA
01063; \href{mailto:aacharya@smith.edu}{\nolinkurl{aacharya@smith.edu}}\\
$^{2}$ \quad Smith
College; \href{mailto:dcaravela@smith.edu}{\nolinkurl{dcaravela@smith.edu}}\\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
Tel.: +XX-000-00-0000.}

@@

% Simple summary
\simplesumm{A Simple summary goes here.}

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research
articles, abstracts should give a pertinent overview of the work. We
strongly encourage authors to use the following style of structured
abstracts, but without headings: 1) Background: Place the question
addressed in a broad context and highlight the purpose of the study; 2)
Methods: Describe briefly the main methods or treatments applied; 3)
Results: Summarize the article's main findings; and 4) Conclusion:
Indicate the main conclusions or interpretations. The abstract should be
an objective representation of the article, it must not contain results
which are not presented and substantiated in the main text and should
not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
keywords specific to the article, yet reasonably common within the
subject discipline.).}

@@

A recidivist is a term to describe criminals who re-offend.

@@

The data we are using for this project is the Correctional Offender
Management Profiling for Alternative Sanctions (COMPAS) Recidivism Risk
Scores dataset from AIF360. Northpointe created COMPAS as a commercial
risk assessment tool to score defendants on their potential recidivism
and violent recidivism risk. The COMPAS dataset we are using has 6,167
rows and each row represents an arrest charge for a defendant. We also
have data on the defendant's age, race, sex, what they were charged
with, and whether or not the defendant ultimately recidivated.

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(}\FunctionTok{rnorm}\NormalTok{(}\DecValTok{10}\NormalTok{), }\FunctionTok{rnorm}\NormalTok{(}\DecValTok{10}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x }\OtherTok{\textless{}{-}}\NormalTok{ tibble}\SpecialCharTok{::}\FunctionTok{tribble}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\StringTok{\textasciigrave{}}\AttributeTok{Title 1}\StringTok{\textasciigrave{}}\NormalTok{, }\SpecialCharTok{\textasciitilde{}}\StringTok{\textasciigrave{}}\AttributeTok{Title 2}\StringTok{\textasciigrave{}}\NormalTok{, }\SpecialCharTok{\textasciitilde{}}\StringTok{\textasciigrave{}}\AttributeTok{Title 3}\StringTok{\textasciigrave{}}\NormalTok{,}
\StringTok{"entry 1"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"data"}\NormalTok{,}
\StringTok{"entry 2"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"data"}
\NormalTok{)}

\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(x, }\AttributeTok{caption =} \StringTok{"This is a table caption. Tables should be placed in the main text near to the first time they are cited.}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{label\{tab:mytable\}"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{All sources of funding of the study should be
disclosed. Please clearly indicate grants that you have received in
support of your research work. Clearly state if you received funds for
covering the costs to publish in open access.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short
paragraph specifying their individual contributions must be provided.
The following statements should be used ``X.X. and Y.Y. conceive and
designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
analyzed the data; W.W. contributed reagents/materials/analysis tools;
Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state `The authors
declare no conflict of interest.' Authors must identify and declare any
personal circumstances or interest that may be perceived as
inappropriately influencing the representation or interpretation of
reported research results. Any role of the funding sponsors in the
design of the study; in the collection, analyses or interpretation of
data in the writing of the manuscript, or in the decision to publish the
results must be declared in this section. If there is no role, please
state `The founding sponsors had no role in the design of the study; in
the collection, analyses, or interpretation of data; in the writing of
the manuscript, an in the decision to publish the results'.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
LD & linear dichroism \\
\end{tabular}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds \ldots\ldots{} are
available from the authors.}

>>>>

% Authors, for the paper (add full first names)
\Author{$^{}$}

% Authors, for metadata in PDF
\AuthorNames{}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Statistical and Data Sciences Smith College Northampton, MA 01063; \\
$^{2}$ \quad ; \href{mailto:aacharya@smith.edu}{\nolinkurl{aacharya@smith.edu}}\\
$^{3}$ \quad ; \href{mailto:dcaravela@smith.edu}{\nolinkurl{dcaravela@smith.edu}}\\
$^{4}$ \quad ; \href{mailto:ekim89@smith.edu}{\nolinkurl{ekim89@smith.edu}}\\
$^{5}$ \quad ; \href{mailto:ekornberg@smith.edu}{\nolinkurl{ekornberg@smith.edu}}\\
$^{6}$ \quad ; \href{mailto:enesmith@smith.edu}{\nolinkurl{enesmith@smith.edu}}\\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
Tel.: +XX-000-00-0000.}

@@

% Simple summary

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A variety of disciplines use risk assessment instruments to help humans
make data-driven decisions. Northpointe, a software company, created a
risk assessment instrument known as the Correctional Offender Management
Profiling for Alternative Sanctions (COMPAS). COMPAS uses various
behavioral and psychological metrics related to recidivism to assist
justice systems in assessing a defendant's potential recidivism risk.
ProPublica published an article which concludes that the biases in the
criminal justice system are reflected in the COMPAS software. Using a
human rights framework adopted from the organization Women at the Table,
we use various debiasing algorithms to analyze both sides of the
argument between Northpointe and ProPublica and determine the level and
extent of racial bias in the COMPAS algorithm.}

% Keywords

@@

Women @ the Table, the sponsor organization for this project, is ``a
growing, global gender equality \& democracy CSO based in Geneva,
Switzerland focused on advancing feminist systems change by using the
prism of technology, innovation \& AI exercising leverage points in
technology, the economy, sustainability \& democratic governance''
\citep{noauthor_womenthetable_nodate}. We have been asked to collaborate
on their AI \& Equality \citep{noauthor_ai_nodate} initiative, tasked
with debiasing the COMPAS algorithm
\citep{noauthor_aif360datasetscompasdataset_2018} and producing a
corresponding data story that will be added to their library.

The Correctional Offender Management Profiling for Alternative Sanctions
(COMPAS) algorithm was created by the private for-profit company
Northpointe, also known by its parent company Equivant
\citep{equivant_faq_nodate}, to predict defendants' risk of recidivism.
It generates a score that classifies defendants' risk of recidivism as
either low, medium, or high \citep{angwin2016machine}. Jurisdictions
across the United States use the COMPAS risk assessment instrument. In
2016, ProPublica published a piece that analyzed the methods and
algorithms used by Northpointe to uncover racial biases in defendants'
scores \citep{angwin2016machine}. Their analysis looks at the
distribution of decile COMPAS scores among Black and white defendants.
ProPublica concludes, after using a statistical parity metric on false
positives or false negatives, that the algorithm is racially biased
\citep{larson2016we}. Northpointe denies the allegations of racial bias,
conducting their own analyses based on different statistical parity
metrics \citep{equivant_response_2018}. Since then, the two parties have
had several exchanges, maintaining their original arguments. Currently,
the two parties' disagreement focuses on pretrial Risk Assessment
Instruments (RAIs). ProPublica maintains that there are biases in the
outcome values, protected attributes, and covariates during
Northpointe's data processing phase. ProPublica accounts for these
biases in their analyses, and Northepointe's response, highlights how
ProPublica did not account for base rates of recidivism in their
analysis, which are important to understand initial percentages without
the presence of other information.

Our project builds on Women at the Table's various debiasing algorithms
to conduct our own analyses on the COMPAS dataset. Based on this
analysis, we employ a human rights framework to contribute to the
ongoing ProPublica and Northpointe debate and investigate whether or to
what extent there is racial bias in the COMPAS algorithm. With a solid
understanding of the two sides, we aim to pinpoint the shortcomings of
both arguments and correct them in our analyses. We will use various
machine learning algorithms including logistic regression, cross
validation, and lasso and ridge techniques to choose models. We will
summarize our results using the JupyterNotebook framework from Women at
the Table, to be used by members of the organization to teach in a
workshop setting. We hope that our findings will highlight the
importance of checking statistical analyses using varied methods and
contribute to the ongoing discussion of the effects of machine biases in
the justice system.

@@

The data we are using for this project is the COMPAS General Recidivism
Risk Scores dataset from ProPublica used in their original analysis
\citep{larson_propublicacompas-analysiscompas-scores-two-yearscsv_2022}.
The COMPAS dataset we are using is from AI Fairness 360 (AIF360) toolkit
\citep{noauthor_trusted-ai_360} which does the same initial
preprocessing as ProPublica. The raw data has 6,167 rows and each row
represents an arrest charge for a defendant. ProPublica's COMPAS data
includes the defendant's age, race, sex, what they were charged with,
and whether or not the defendant ultimately recidivated within a
two-year period after their arrest. For the purposes of our project,
which endeavors to evaluate the differing effects of the COMPAS
algorithm on white defendants and Black defendants, we have filtered the
data to only include individuals whose race is listed as Caucasian or
African-American. Our data therefore has 5,723 rows (Figure
\ref{fig:table snip}), with the below distributions of race (Figure
\ref{fig:race plot}), age (Figure \ref{fig:age plot}), and two year
recidivism rate (Figures \ref{fig:recid plot} \&
\ref{fig:recid race plot}).

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/table_snippet.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=27.78in]{/Users/elisabethnesmith/womenatthetable/images/table_snippet}

\caption{This table is a snippet the data set we will be using.}\label{fig:table snip}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/race_bar_plot.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=12.69in]{/Users/elisabethnesmith/womenatthetable/images/race_bar_plot}

\caption{This plot shows the distribution of defendant races.}\label{fig:race plot}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/race_age_plot.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=11.61in]{/Users/elisabethnesmith/womenatthetable/images/race_age_plot}

\caption{This plot shows the distribution of defendant ages by race.}\label{fig:age plot}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/recid_bar_plot.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=11.28in]{/Users/elisabethnesmith/womenatthetable/images/recid_bar_plot}

\caption{This plot shows the distribution of two year recidivism outcomes.}\label{fig:recid plot}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/race_recid_plot.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=11.31in]{/Users/elisabethnesmith/womenatthetable/images/race_recid_plot}

\caption{This plot shows the distribution of two year recidivism outcomes by race.}\label{fig:recid race plot}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\NormalTok{), }\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x <-}\StringTok{ }\NormalTok{tibble}\OperatorTok{::}\KeywordTok{tribble}\NormalTok{(}\OperatorTok{~}\StringTok{`}\DataTypeTok{Title 1}\StringTok{`}\NormalTok{, }\OperatorTok{~}\StringTok{`}\DataTypeTok{Title 2}\StringTok{`}\NormalTok{, }\OperatorTok{~}\StringTok{`}\DataTypeTok{Title 3}\StringTok{`}\NormalTok{,}
\StringTok{"entry 1"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"data"}\NormalTok{,}
\StringTok{"entry 2"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"data"}
\NormalTok{)}

\NormalTok{knitr}\OperatorTok{::}\KeywordTok{kable}\NormalTok{(x, }\DataTypeTok{caption =} \StringTok{"This is a table caption. Tables should be placed in the main text near to the first time they are cited.}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{label\{tab:mytable\}"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
